### 2022-06-13 manuscript.tex
Merge pull request #238 from SORTEE-Github-Hackathon/robcrystalornelas-fix-github-image [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8c2aac108bf451c48272ca35f8bd93bfd6a499fd.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/8c2aac108bf451c48272ca35f8bd93bfd6a499fd/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/2490483271

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3b6215a8c54e5db5b4b561ab67693bb5c7fc5f73}{SORTEE-Github-Hackathon/manuscript@3b6215a}
on June 13, 2022.

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/8c2aac108bf451c48272ca35f8bd93bfd6a499fd/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/8c2aac108bf451c48272ca35f8bd93bfd6a499fd}{SORTEE-Github-Hackathon/manuscript@8c2aac1}
on June 13, 2022.
